### 2018-09-21 articleSFDS.tex
Psi Figure 7

\begin{figure}[htbp!]
\begin{center}
  \begin{tabular}{cccc}
&  $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_4'$ \\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{figR/model3/densitySigD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/densitySigD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densitySigD.pdf}\\
	&\multicolumn{3}{c}{$\sigma_{\boldsymbol{\delta}}^2$}\\
	&&&\\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{figR/model3/densityPsiD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/densityPsiD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densityPsiD.pdf}\\
	&\multicolumn{2}{c}{$\psi_{\boldsymbol{\delta}}$}\\
  \end{tabular}   
\caption{\textit{Prior} (in blue) and posterior (in red) densities of $\sigma_{\boldsymbol{\delta}}^2$ and $\psi_{\boldsymbol{\delta}}$ for $\mathcal{M}_3$, $\mathcal{M}_4$ and $\mathcal{M}_4'$.}
\label{fig:comparisionDensities2}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp!]
\begin{center}
  \begin{tabular}{cccc}
&  $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_4'$ \\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{figR/model3/densitySigD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/densitySigD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densitySigD.pdf}\\
	&\multicolumn{3}{c}{$\sigma_{\boldsymbol{\delta}}^2$}\\
	&&&\\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{figR/model3/densityPsiD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/densityPsiD.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densityPsiD.pdf}\\
	&\multicolumn{3}{c}{$\psi_{\boldsymbol{\delta}}$}\\
  \end{tabular}   
\caption{\textit{Prior} (in blue) and posterior (in red) densities of $\sigma_{\boldsymbol{\delta}}^2$ and $\psi_{\boldsymbol{\delta}}$ for $\mathcal{M}_3$, $\mathcal{M}_4$ and $\mathcal{M}_4'$.}
\label{fig:comparisionDensities2}
\end{center}
\end{figure}
